\documentclass[11pt]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}

\begin{document}

\section{White Box Testing (25 marks)}

This report documents the white-box testing performed on the MoneyPoly board game implementation. The program manages players, money, property purchases, rent payments, jail, cards and the main game loop. There were several logical issues in the original code; they were analysed using control-flow driven tests and corrected, with each significant bug captured as an ``Error~
#'' commit.

\subsection{Control Flow Graph (1.1)}

The Control Flow Graph (CFG) was drawn by hand for the core of the game logic, focusing on the following functions in \texttt{game.py}:

\begin{itemize}
  \item \texttt{Game.play\_turn}
  \item \texttt{Game.\_move\_and\_resolve}
  \item \texttt{Game.handle\_property\_tile}
  \item \texttt{Game.\_handle\_jail\_turn}
  \item \texttt{Game.auction\_property}, \texttt{Game.trade}
  \item Card handlers in \texttt{apply\_card} (e.g. \texttt{move\_to}, \texttt{birthday}, \texttt{collect\_from\_all})

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

Each basic block (straight-line code with no internal branches) is represented as a node, labelled with a short description such as ``P1: start of \texttt{play\_turn}'', ``M3: tile type is \texttt{income\_tax}'', or ``J2: voluntary jail fine?''. Directed edges indicate control flow between these nodes. For example:

\begin{itemize}
  \item In \texttt{play\_turn}, there are separate outgoing edges for:
  \begin{itemize}
    \item the case where the current player starts the turn in jail and control transfers to \texttt{\_handle\_jail\_turn} and then to \texttt{advance\_turn};
    \item the triple-doubles path, where \texttt{doubles\_streak} reaches~3 and the player is sent directly to jail;
    \item the normal movement path, where a single roll leads to \texttt{\_move\_and\_resolve}, and then either an extra turn (doubles) or \texttt{advance\_turn} (non-doubles).
  
    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}
  \item In \texttt{\_move\_and\_resolve}, a decision node branches on the tile type: \texttt{go\_to\_jail}, \texttt{income\_tax}, \texttt{luxury\_tax}, \texttt{free\_parking}, \texttt{chance}, \texttt{community\_chest}, \texttt{railroad}, and \texttt{property}, before ending at a node that calls \texttt{\_check\_bankruptcy}.
  \item Separate subgraphs were drawn for \texttt{handle\_property\_tile} and \texttt{\_handle\_jail\_turn}, capturing user choices (buy/auction/skip, yes/no to fines, use card or not) and their effects on game state.

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

The resulting CFG diagram (attached as a figure in the full report) was then used to plan the white-box tests in Section~\ref{sec:white-box-tests}.

\subsection{Code Quality Analysis with \texttt{pylint} (1.2)}

\label{sec:code-quality}

The codebase was iteratively improved using \texttt{pylint}. Each iteration is recorded as a commit of the form ``Iteration~\#:\textless{}What You Changed\textgreater{}'' in the Git history (see the screenshots in the appendix). Early iterations removed purely stylistic issues; the later iterations (especially Iterations~25--30 shown in the log) focused on refactoring the design so that the control flow is easier to understand, reason about with a CFG, and exercise with unit tests.

Key improvements from these later refactoring iterations are summarised below.

\begin{itemize}
  \item \textbf{Consistent documentation and naming.}  Docstrings were added to all modules and to important classes and methods (for example \texttt{Game.run}, \texttt{Game.play\_turn}, \texttt{Game.\_handle\_jail\_turn}, the card handlers in \texttt{apply\_card}, and helper classes such as \texttt{PropertyGroup}, \texttt{Bank}, and \texttt{Dice}).  Parameter names were aligned across modules (e.g. always using \texttt{player}, \texttt{amount}, \texttt{property}) so that the meaning of each branch is explicit and easy to relate to the CFG.

  \item \textbf{Cleaning up imports and dead code.}  Unused or redundant imports were removed from several modules (for example \texttt{os}, \texttt{sys} and other unused utilities), and unused constants and never-taken branches were eliminated.  Some legacy logic that was no longer reachable (e.g. old menu options and duplicate mortgage paths) was removed.  This reduced the size of the effective CFG and ensured white-box tests focus only on behaviour that can actually occur at runtime.

  \item \textbf{Safer, clearer branch logic.}  Several refactorings were applied to make decisions and side effects more explicit.  Iteration~30, for example, refactored \texttt{apply\_card} to reduce the amount of branching while keeping every card action (collect, pay, jail, jail\_free, move\_to, birthday, collect\_from\_all) visible as a separate, testable case in the CFG.  In addition:
  \begin{itemize}
    \item In \texttt{Game.handle\_property\_tile}, the user choices were normalised to explicit options ``b'' (buy), ``a'' (auction), ``s'' (skip), with a separate branch for invalid input.  Previously, invalid input was tangled with the skip behaviour; now each outcome is its own branch in the CFG.
    \item In the mortgage and unmortgage functions, nested \texttt{if}/\texttt{else} ladders were simplified into clear sequential checks (ownership, mortgage status, affordability).  Each failure mode now returns early with a single responsibility, which matches one row in the branch--test map.
    \item The financial operations in tax tiles, rent, card payments and jail fines were rephrased in terms of helper methods like \texttt{Player.deduct\_money}, \texttt{Player.add\_money} and \texttt{Bank.collect}.  Together with later bug fixes (captured as ``Error~\#'' commits), this made it impossible to silently push a player below zero without going through the shared bankruptcy check.
  
    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

  \item \textbf{Clarifying stateful components.}  Iterations~26 and~28 specifically targeted overgrown classes by reducing the number of instance attributes on \texttt{Game} and \texttt{Player} to seven each.  Attributes like \texttt{doubles\_streak} in \texttt{Dice}, jail-related state in \texttt{Player} and \texttt{Game}, and mortgage flags in \texttt{Property} were clearly initialised, documented and accessed through helper methods.  For example, the jail turn handling was concentrated in \texttt{Game.\_handle\_jail\_turn} instead of being spread across \texttt{play\_turn}, and board ownership queries were consistently routed through \texttt{Board.get\_property\_at} and \texttt{Board.is\_purchasable}.  This reduced hidden coupling and made it much easier to write targeted tests for jail, rent, auctions and triple doubles.

  \item \textbf{Structural refactoring for testability.}  Iteration~25 refactored the monolithic \texttt{Game} class by extracting interactive menu logic into a separate \texttt{Menu} abstraction.  In a later clean-up pass this extra class was simplified again into a small helper function / action handler (leaving \texttt{Game} focused on game rules and state), but the separation between menu handling and core game mechanics remained.  Later iterations removed the old \texttt{Decks} class (Iteration~27) in favour of the focused \texttt{CardDeck} type, and introduced a dedicated \texttt{PropertySpec} with documented accessors for property metadata (Iteration~29).  More generally, the responsibilities of core components were tightened so that each method has a single, testable purpose:
  \begin{itemize}
    \item The main turn logic was split between \texttt{Game.play\_turn} (high-level turn orchestration), \texttt{Game.\_move\_and\_resolve} (movement and tile resolution), and helper methods such as \texttt{handle\_property\_tile}, \texttt{auction\_property}, \texttt{trade} and \texttt{\_check\_bankruptcy}.  This reduced very long functions into smaller units with clear entry and exit points.
    \item User-interface concerns (printing menus, standings, board ownership) were confined to the UI layer and to menu helper methods, while pure game-state changes live in the \texttt{Game}, \texttt{Player}, \texttt{Board}, \texttt{Property} and \texttt{Bank} classes.  This separation allowed the tests to exercise logic branches without asserting on text output.
    \item Supporting classes like \texttt{CardDeck}, \texttt{Dice} and \texttt{PropertyGroup} were given small, well-defined APIs so that their behaviour (reshuffling, doubles streaks, group rent calculation) can be tested independently of the rest of the game.
  
    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

After these refactoring iterations, \texttt{pylint} reports were clean (overall score 10/10), complex functions were broken into smaller, well-named helpers, and the resulting structure provided a stable foundation for drawing the CFG and designing the systematic white-box test suite in Section~\ref{sec:white-box-tests}.

\subsection{White Box Test Cases (1.3)}
\label{sec:white-box-tests}

White-box tests were designed using the CFG and the refactored code from Section~\ref{sec:code-quality}.  The goals were:

\begin{itemize}
  \item to cover all important branches (every decision path) in the game logic;
  \item to exercise key variable states that affect behaviour (e.g. balances around zero, ownership status, jail turns, doubles streak);
  \item to include relevant edge cases such as exact-boundary values (exact price, exact fine), zero values, and unusual player inputs.

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

The tests are organised by feature: turn management, movement and tiles, property handling, rent and trade, jail, taxes and bankruptcy, and winner selection.  For each bug discovered, the failing test was added first and the fix was then implemented and committed as an ``Error~\#'' commit.  Examples include:

\begin{itemize}
  \item Incorrect card deck reshuffling when all cards were drawn.
  \item \texttt{pay\_rent} not crediting the property owner and not triggering bankruptcy elimination.
  \item \texttt{handle\_property\_tile} treating any non-``b''/``a'' input as an implicit skip; tests forced the logic to require explicit ``s'' to skip and to handle invalid inputs gracefully.
  \item Income/luxury tax and jail fines originally allowed the bank to collect the full tax or fine even when the player had less money, leaving the player negative and the bank with more money than existed.  New tests required the bank to collect only the player's remaining balance; the code was fixed accordingly.
  \item Several guard paths in jail and trade menus (no other players, no properties, invalid indices) which were previously untested and are now covered by explicit tests.

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

\subsubsection*{Summary of discovered ``Error~\#'' fixes}

Table~\ref{tab:errors} summarises all of the ``Error~\#'' commits recorded during testing, the underlying problem, and the area of the code that was changed.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.14\textwidth} >{\raggedright\arraybackslash}p{0.33\textwidth} >{\raggedright\arraybackslash}p{0.38\textwidth}}
\caption{Discovered errors and corresponding fixes}\label{tab:errors}\\\hline
\textbf{Error} & \textbf{Problem discovered by tests} & \textbf{Fix (modules / functions)} \\ \hline
\endfirsthead
\hline
\textbf{Error} & \textbf{Problem discovered by tests} & \textbf{Fix (modules / functions)} \\ \hline
\endhead
Error 1 & Bankruptcy handling for birthday and collect\_from\_all cards did not correctly eliminate players or clear their properties. & Updated card handlers and bankruptcy logic so that birthday / collect\_from\_all cards call the shared bankruptcy check and remove insolvent players from the game. \\ \hline
Error 2 & Birthday and collect\_from\_all card behaviour around players with low balances was inconsistent with the rules (some players were being over-charged or wrongly bankrupted). & Adjusted card logic so players who cannot afford the gift or contribution are treated consistently, aligning with the new bankruptcy rules and tests in tests/test\_bankruptcy\_cards.py. \\ \hline
Error 3 & Winner selection, Go salary on passing/landing on Go, and exact-balance property purchases behaved incorrectly in edge cases. & Fixed \texttt{Game.find\_winner}, \texttt{Player.move} and property purchase checks so that Go salary is paid exactly once when appropriate and players with exact balances can still buy property; winner now uses correct net worth. \\ \hline
Error 4 & \texttt{Bank.collect} accepted zero or negative amounts, which allowed some code paths to accidentally ``refund'' or do meaningless collections. & Added validation in \texttt{Bank.collect} so that it ignores non-positive amounts and only adjusts balances when a real payment is made. \\ \hline
Error 5 & Jail fine payment and bankruptcy handling were inconsistent: players could remain in the game or move even after they could not afford fines. & Centralised fine processing in \texttt{Game.\_handle\_jail\_turn} and the bankruptcy helper so that fines use the player's remaining balance and eliminate the player cleanly when they cannot pay. \\ \hline
Error 6 & \texttt{CardDeck} did not correctly handle empty decks: \texttt{draw}, \texttt{cards\_remaining} and \texttt{\_\_repr\_\_} behaved incorrectly once all cards were used. & Updated \texttt{CardDeck.draw} and related attributes so that drawing from an empty deck returns \texttt{None}, keeps \texttt{cards\_remaining} at zero, and still allows a safe string representation. \\ \hline
Error 7 & \texttt{PropertyGroup} full-set ownership logic was wrong, so group rent and ownership counts were miscomputed. & Corrected \texttt{PropertyGroup.all\_owned\_by} and owner-count calculations so that full-group ownership and doubled rent are computed exactly as intended. \\ \hline
Error 8 & Two related issues: (a) \texttt{Bank.give\_loan} did not always reduce the bank's funds correctly, and (b) \texttt{unmortgage\_property} allowed players to unmortgage even when they could not afford the cost. & Fixed \texttt{Bank.give\_loan} so that bank funds and player balances change symmetrically, and tightened the affordability check in \texttt{Game.unmortgage\_property} so that unmortgaging only succeeds when the player has enough money. \\ \hline
Error 9 & After all cards had been drawn, \texttt{CardDeck} did not automatically reshuffle the discard pile and restart the sequence. & Changed \texttt{CardDeck} to auto-reshuffle when exhausted and reset the internal index, with tests covering reshuffle behaviour. \\ \hline
Error 10 & \texttt{pay\_rent} sometimes failed to transfer rent to the property owner and did not always bankrupt tenants who could not pay. & Reworked \texttt{Game.pay\_rent} so that rent is always deducted from the tenant, credited to the owner, and routed through bankruptcy checks when the tenant cannot afford the full amount. \\ \hline
Error 11 & Income tax tile allowed the bank to collect the full fixed amount even when a player had less money, leaving the player with a negative balance. & Updated income tax handling in \texttt{Game.\_move\_and\_resolve} so the bank only collects up to the player's remaining balance. \\ \hline
Error 12 & Luxury tax tile similarly allowed the bank to over-collect from a player, causing negative balances. & Updated luxury tax handling to cap deductions at the player's current balance, triggering clean bankruptcy. \\ \hline
Error 13 & Jail fines allowed the bank to collect full amounts from players who couldn't afford it. & Updated jail fine logic in \texttt{Game.\_handle\_jail\_turn} to collect only up to available balance and cleanly eliminate bankrupt players. \\ \hline
Error 14 & Property tile selection prompted for Buy (b), Auction (a), or Skip (s), but any invalid letter or symbol was silently accepted, failing to clear the prompt and instead defaulting to an accidental skip. & Updated \texttt{Game.handle\_property\_tile} to loop continuously on invalid input, requiring the user to explicitly enter a valid character before proceeding. \\ \hline
\end{longtable}

To keep the link between the implementation and the tests explicit, a separate file \texttt{BRANCH\_TEST\_MAP.md} was maintained in the repository.  It documents, for each important branch, which test(s) exercise it.  The next subsection presents a LaTeX version of the main part of that mapping for the core \texttt{Game} logic.

\subsection*{Branch-to-Test Mapping for Core Game Logic}

Tables~\ref{tab:game-playturn}--\ref{tab:game-jail} summarise the relationship between the main branches in \texttt{game.py} and the tests that cover them.  (The full map, including other modules, is available in \texttt{BRANCH\_TEST\_MAP.md}.)

\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.55\textwidth}}
\caption{Branches in \texttt{Game.play\_turn} and related helpers}\label{tab:game-playturn}\\\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endfirsthead
\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endhead
Player starts turn in jail: call \texttt{\_handle\_jail\_turn} then \texttt{advance\_turn} and return & \texttt{test\_play\_turn\_calls\_jail\_handler\_for\_jailed\_player} (tests/test\_game\_ui\_main.py) \\ \hline
\texttt{doubles\_streak} $\geq 3$: player sent to jail and turn advanced & \texttt{test\_play\_turn\_triple\_doubles\_sends\_to\_jail} (tests/test\_game\_ui\_main.py) \\ \hline
Non-doubles roll: \texttt{\_move\_and\_resolve} called and \texttt{advance\_turn} executed & \texttt{test\_play\_turn\_moves\_player\_and\_advances\_turn\_for\_non\_doubles} (tests/test\_game\_ui\_main.py) \\ \hline
Doubles (but not triple): \texttt{\_move\_and\_resolve} called and turn not advanced & \texttt{test\_play\_turn\_doubles\_gives\_extra\_turn\_without\_advancing\_player} (tests/test\_game\_ui\_main.py) \\ \hline
\end{longtable}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.55\textwidth}}
\caption{Branches in \texttt{Game.\_move\_and\_resolve} and tile handling}\label{tab:game-move-resolve}\\\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endfirsthead
\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endhead
Tile is \texttt{go\_to\_jail}: player sent directly to jail square & \texttt{test\_go\_to\_jail\_tile\_sends\_player\_to\_jail} (tests/test\_taxes\_and\_rent.py) \\ \hline
Tile is \texttt{income\_tax}: deduct up to player balance, bank collects same, may bankrupt & \texttt{test\_income\_tax\_reduces\_balance\_but\_not\_eliminate\_when\_affordable}, \texttt{test\_income\_tax\_can\_bankrupt\_and\_eliminate\_player} (tests/test\_taxes\_and\_rent.py) \\ \hline
Tile is \texttt{luxury\_tax}: deduct up to player balance, bank collects same, may bankrupt & \texttt{test\_luxury\_tax\_can\_bankrupt\_and\_eliminate\_player} (tests/test\_taxes\_and\_rent.py) \\ \hline
Tile is \texttt{free\_parking}: no change in balance or jail status & \texttt{test\_free\_parking\_tile\_has\_no\_effect} (tests/test\_taxes\_and\_rent.py) \\ \hline
Tile is \texttt{chance}: draw from chance deck and apply card & Card effects covered in tests/test\_bankruptcy\_cards.py; deck behaviour in tests/test\_dice\_and\_cards.py (the branch itself is a thin wrapper) \\ \hline
Tile is \texttt{community\_chest}: draw from community chest deck and apply card & Same as chance: card and deck tests exercise this path indirectly \\ \hline
Tile is \texttt{property}: look up property and call \texttt{handle\_property\_tile} if non-\texttt{None} & Property landing via movement and cards tested in tests/test\_winner\_and\_movement\_and\_purchase.py and \texttt{test\_move\_to\_card\_calls\_handle\_property\_tile\_when\_landing\_on\_property} (tests/test\_bankruptcy\_cards.py) \\ \hline
Final bankruptcy check after movement and tile effects & Tax, rent, card, and jail bankruptcy tests (tests/test\_taxes\_and\_rent.py, tests/test\_trade\_and\_rent.py, tests/test\_bankruptcy\_cards.py, tests/test\_jail\_and\_cards.py) \\ \hline
\end{longtable}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.55\textwidth}}
\caption{Branches in property, rent, trade, and jail logic}\label{tab:game-jail}\\\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endfirsthead
\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endhead
Unowned property; input ``b'': attempt to buy via \texttt{buy\_property} & \texttt{test\_can\_buy\_property\_with\_exact\_balance}, \texttt{test\_buy\_property\_fails\_when\_balance\_below\_price} (tests/test\_winner\_and\_movement\_and\_purchase.py) \\ \hline
Unowned property; input ``a'': call \texttt{auction\_property} & Property/auction interaction tests in tests/test\_winner\_and\_movement\_and\_purchase.py and auction tests in tests/test\_game\_ui\_main.py \\ \hline
Unowned property; input ``s'': explicit skip, no buy or auction & \texttt{test\_handle\_property\_tile\_skip\_with\_s\_leaves\_property\_unowned} (tests/test\_winner\_and\_movement\_and\_purchase.py) \\ \hline
Unowned property; invalid input: print message and default to skip & \texttt{test\_handle\_property\_tile\_invalid\_choice\_defaults\_to\_skip} (tests/test\_winner\_and\_movement\_and\_purchase.py) \\ \hline
Property owned by current player: no rent charged & \texttt{test\_landing\_on\_owned\_property\_does\_not\_charge\_rent} (tests/test\_winner\_and\_movement\_and\_purchase.py) \\ \hline
Property owned by another player: rent deducted from tenant, credited to owner, may bankrupt tenant & \texttt{test\_pay\_rent\_transfers\_to\_owner}, \texttt{test\_pay\_rent\_can\_bankrupt\_tenant} (tests/test\_trade\_and\_rent.py) \\ \hline
Trade fails when seller does not own property or buyer cannot afford cash amount & \texttt{test\_trade\_fails\_when\_seller\_does\_not\_own\_property}, \texttt{test\_trade\_fails\_when\_buyer\_cannot\_afford} (tests/test\_trade\_and\_rent.py) \\ \hline
Successful trade: property transferred, balances updated & \texttt{test\_trade\_succeeds\_and\_transfers\_property\_and\_cash} (tests/test\_trade\_and\_rent.py) \\ \hline
Jail card branch: if player has a card and confirms, use card, release and move & \texttt{test\_use\_get\_out\_of\_jail\_free\_card\_with\_confirm\_yes} (tests/test\_jail\_and\_cards.py) \\ \hline
Voluntary fine branch: pay fine (up to balance), release and move when still solvent & \texttt{test\_jail\_turn\_voluntary\_fine\_deducts\_from\_player} (tests/test\_jail\_and\_cards.py) \\ \hline
Voluntary fine bankruptcy: player eliminated, bank only collects available cash, no movement & \texttt{test\_jail\_voluntary\_fine\_can\_bankrupt\_and\_prevent\_movement} (tests/test\_jail\_and\_cards.py) \\ \hline
Mandatory fine after three turns: solvent player pays, is released and moves & \texttt{test\_jail\_turn\_mandatory\_fine\_after\_three\_turns} (tests/test\_jail\_and\_cards.py) \\ \hline
Mandatory fine bankruptcy: player eliminated, bank only collects available cash, no movement & \texttt{test\_jail\_mandatory\_fine\_bankruptcy\_only\_collects\_available\_cash} (tests/test\_jail\_and\_cards.py) \\ \hline
\end{longtable}

Finally, for movement-specific player state, \texttt{Player.move} edge cases are covered by:

\begin{itemize}
  \item \texttt{test\_move\_past\_go\_awards\_salary} (wrapping around the board and passing Go once), and
  \item \texttt{test\_move\_lands\_exactly\_on\_go\_awards\_salary} (landing exactly on Go).

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

\subsection*{Full Branch-to-Test Mapping (All Modules)}

The following table reproduces the full branch-to-test mapping used during white-box test design, covering the main modules in the MoneyPoly codebase.

\begin{longtable}{>{\raggedright\arraybackslash}p{0.38\textwidth} >{\raggedright\arraybackslash}p{0.55\textwidth}}
\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endfirsthead
\hline
\textbf{Branch / Condition} & \textbf{Tests covering it} \\ \hline
\endhead
\multicolumn{2}{l}{\textbf{moneypoly.game: apply\_card and card handlers}} \\ \hline
card is \texttt{None} returns immediately & \texttt{test\_empty\_deck\_draw\_and\_peek} (draw returns \texttt{None}, then \texttt{apply\_card} effectively no-ops via callers) in tests/test\_dice\_and\_cards.py \\ \hline
Unknown action prints a warning and returns without effect & \texttt{test\_apply\_card\_unknown\_action\_warns\_and\_does\_nothing} in tests/test\_game\_ui\_main.py \\ \hline
``collect'' card: bank pays player & \texttt{test\_collect\_card\_pays\_from\_bank\_to\_player} in tests/test\_bankruptcy\_cards.py \\ \hline
``pay'' card: player pays bank & \texttt{test\_pay\_card\_charges\_player\_and\_credits\_bank} in tests/test\_bankruptcy\_cards.py \\ \hline
``jail'' card: send player directly to jail & \texttt{test\_jail\_card\_sends\_player\_directly\_to\_jail} in tests/test\_bankruptcy\_cards.py \\ \hline
``jail\_free'' card: increment jail card count & \texttt{test\_jail\_free\_card\_increases\_jail\_card\_count} in tests/test\_bankruptcy\_cards.py \\ \hline
``move\_to'' card moves player and pays Go salary when passing Go & \texttt{test\_move\_to\_card\_moves\_player\_and\_awards\_go\_salary\_when\_passing} in tests/test\_bankruptcy\_cards.py \\ \hline
``move\_to'' card landing on property calls \texttt{handle\_property\_tile} & \texttt{test\_move\_to\_card\_calls\_handle\_property\_tile\_when\_landing\_on\_property} in tests/test\_bankruptcy\_cards.py \\ \hline
``birthday'' card skips players who cannot afford the gift and never bankrupts them & \texttt{test\_birthday\_skips\_players\_who\_cannot\_afford\_gift} in tests/test\_bankruptcy\_cards.py \\ \hline
``collect\_from\_all'' charges all players and can bankrupt them & \texttt{test\_collect\_from\_all\_can\_bankrupt\_and\_eliminate\_other\_players} in tests/test\_bankruptcy\_cards.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: interactive\_menu}} \\ \hline
Choice 0: exit menu loop & \texttt{test\_interactive\_menu\_standings\_and\_exit} in tests/test\_game\_ui\_main.py \\ \hline
Choice 1: call \texttt{ui.print\_standings} & \texttt{test\_interactive\_menu\_standings\_and\_exit} in tests/test\_game\_ui\_main.py \\ \hline
Choice 2: call \texttt{ui.print\_board\_ownership} & \texttt{test\_interactive\_menu\_board\_and\_mortgage\_unmortgage\_trade\_loan} in tests/test\_game\_ui\_main.py \\ \hline
Choice 3: call \texttt{\_menu\_mortgage} & \texttt{test\_interactive\_menu\_board\_and\_mortgage\_unmortgage\_trade\_loan} in tests/test\_game\_ui\_main.py \\ \hline
Choice 4: call \texttt{\_menu\_unmortgage} & \texttt{test\_interactive\_menu\_board\_and\_mortgage\_unmortgage\_trade\_loan} in tests/test\_game\_ui\_main.py \\ \hline
Choice 5: call \texttt{\_menu\_trade} & \texttt{test\_interactive\_menu\_board\_and\_mortgage\_unmortgage\_trade\_loan} in tests/test\_game\_ui\_main.py \\ \hline
Choice 6: request loan and call \texttt{bank.give\_loan} when amount $>$ 0 & \texttt{test\_interactive\_menu\_board\_and\_mortgage\_unmortgage\_trade\_loan} in tests/test\_game\_ui\_main.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: mortgage\_property / unmortgage\_property}} \\ \hline
\texttt{mortgage\_property}: player does not own property $\rightarrow$ fail & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{mortgage\_property}: property already mortgaged $\rightarrow$ fail & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{mortgage\_property}: success when owned and not mortgaged & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{unmortgage\_property}: player does not own property $\rightarrow$ fail & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{unmortgage\_property}: property not mortgaged $\rightarrow$ fail & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{unmortgage\_property}: player cannot afford cost $\rightarrow$ fail & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{unmortgage\_property}: success when owned, mortgaged, and affordable & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} in tests/test\_game\_ui\_main.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: \_menu\_mortgage, \_menu\_unmortgage, \_menu\_trade}} \\ \hline
\texttt{\_menu\_mortgage}: no mortgageable properties $\rightarrow$ return & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} indirectly (setup and menu calls) in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_mortgage}: valid index selects property and calls \texttt{mortgage\_property} & \texttt{test\_menu\_mortgage\_and\_unmortgage\_and\_trade} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_unmortgage}: no mortgaged properties $\rightarrow$ return & \texttt{test\_mortgage\_and\_unmortgage\_property\_paths} indirectly in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_unmortgage}: valid index selects property and calls \texttt{unmortgage\_property} & \texttt{test\_menu\_mortgage\_and\_unmortgage\_and\_trade} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_trade}: no other players $\rightarrow$ prints and returns without calling \texttt{trade} & \texttt{test\_menu\_trade\_returns\_when\_no\_other\_players} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_trade}: invalid partner selection index $\rightarrow$ return without calling \texttt{trade} & \texttt{test\_menu\_trade\_returns\_on\_invalid\_partner\_selection} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_trade}: player has no properties $\rightarrow$ prints and returns & \texttt{test\_menu\_trade\_returns\_when\_player\_has\_no\_properties} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_trade}: invalid property index $\rightarrow$ return without calling \texttt{trade} & \texttt{test\_menu\_trade\_returns\_on\_invalid\_property\_selection} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{\_menu\_trade}: happy-path trade (valid partner, property, and cash) calls \texttt{trade} once & \texttt{test\_menu\_mortgage\_and\_unmortgage\_and\_trade} in tests/test\_game\_ui\_main.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: play\_turn}} \\ \hline
Player starts in jail: calls \texttt{\_handle\_jail\_turn} and \texttt{advance\_turn}, then returns & \texttt{test\_play\_turn\_calls\_jail\_handler\_for\_jailed\_player} in tests/test\_game\_ui\_main.py \\ \hline
Dice \texttt{doubles\_streak} $\geq 3$: send player to jail and advance turn & \texttt{test\_play\_turn\_triple\_doubles\_sends\_to\_jail} in tests/test\_game\_ui\_main.py \\ \hline
Non-triple, non-doubles roll: call \texttt{\_move\_and\_resolve}, then \texttt{advance\_turn} & \texttt{test\_play\_turn\_moves\_player\_and\_advances\_turn\_for\_non\_doubles} in tests/test\_game\_ui\_main.py \\ \hline
Doubles (but not triple): call \texttt{\_move\_and\_resolve} and do not advance turn & \texttt{test\_play\_turn\_doubles\_gives\_extra\_turn\_without\_advancing\_player} in tests/test\_game\_ui\_main.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: \_move\_and\_resolve}} \\ \hline
Tile ``go\_to\_jail'': send player to jail & \texttt{test\_go\_to\_jail\_tile\_sends\_player\_to\_jail} in tests/test\_taxes\_and\_rent.py \\ \hline
Tile ``income\_tax'': deduct tax (up to balance), bank collects same, may bankrupt & \texttt{test\_income\_tax\_reduces\_balance\_but\_not\_eliminate\_when\_affordable} and \texttt{test\_income\_tax\_can\_bankrupt\_and\_eliminate\_player} in tests/test\_taxes\_and\_rent.py \\ \hline
Tile ``luxury\_tax'': deduct tax (up to balance), bank collects same, may bankrupt & \texttt{test\_luxury\_tax\_can\_bankrupt\_and\_eliminate\_player} in tests/test\_taxes\_and\_rent.py \\ \hline
Tile ``free\_parking'': no effect on balance or jail state & \texttt{test\_free\_parking\_tile\_has\_no\_effect} in tests/test\_taxes\_and\_rent.py \\ \hline
Tile ``chance'': draw from \texttt{CHANCE\_DECK} and call \texttt{apply\_card} & Indirectly via card tests in tests/test\_bankruptcy\_cards.py and deck tests in tests/test\_dice\_and\_cards.py (card effects and deck mechanics are covered; this branch is a thin wrapper) \\ \hline
Tile ``community\_chest'': draw from \texttt{COMMUNITY\_DECK} and call \texttt{apply\_card} & Same as chance: tests/test\_bankruptcy\_cards.py and tests/test\_dice\_and\_cards.py cover card effects and deck behaviour \\ \hline
Tile ``railroad'': look up property and, if present, call \texttt{handle\_property\_tile} & Currently no real Board properties at railroad positions; effectively dead branch (documented as such) \\ \hline
Tile ``property'': look up property and call \texttt{handle\_property\_tile} if non-\texttt{None} & Property flows (buy/skip/rent) tested via \texttt{handle\_property\_tile} and movement tests in tests/test\_winner\_and\_movement\_and\_purchase.py, plus card move-to property landing in tests/test\_bankruptcy\_cards.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: handle\_property\_tile}} \\ \hline
Property unowned; input ``b'': attempt to buy via \texttt{buy\_property} & \texttt{test\_buy\_property\_succeeds\_when\_affordable} and related tests in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Property unowned; input ``a'': call \texttt{auction\_property} & \texttt{test\_property\_tile\_auction\_path} and other property/auction interaction tests in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Property unowned; input ``s'': skip purchase & \texttt{test\_unowned\_property\_tile\_skip\_with\_s} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Property unowned; invalid input: print invalid choice and skip by default & \texttt{test\_unowned\_property\_tile\_invalid\_choice\_defaults\_to\_skip} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Property owned by current player: no rent collected & \texttt{test\_landing\_on\_owned\_property\_does\_not\_charge\_rent} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Property owned by another player: call \texttt{pay\_rent} & \texttt{test\_pay\_rent\_transfers\_to\_owner} and \texttt{test\_pay\_rent\_can\_bankrupt\_tenant} in tests/test\_trade\_and\_rent.py, plus movement tests in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: buy\_property}} \\ \hline
\texttt{player.balance} $<$ \texttt{prop.price}: cannot afford, returns \texttt{False} & \texttt{test\_buy\_property\_fails\_when\_balance\_less\_than\_price} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Player can afford: deduct price, set owner, add property, bank collects & \texttt{test\_buy\_property\_succeeds\_when\_affordable} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: pay\_rent}} \\ \hline
Property is mortgaged: no rent collected & \texttt{test\_mortgaged\_property\_collects\_no\_rent} in tests/test\_trade\_and\_rent.py \\ \hline
Property has no owner: returns without effect & \texttt{test\_pay\_rent\_no\_owner\_no\_effect} in tests/test\_trade\_and\_rent.py \\ \hline
Normal rent: deduct from tenant, add to owner & \texttt{test\_pay\_rent\_transfers\_to\_owner} in tests/test\_trade\_and\_rent.py \\ \hline
Rent payment can bankrupt tenant and eliminate them & \texttt{test\_pay\_rent\_can\_bankrupt\_tenant} in tests/test\_trade\_and\_rent.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: trade}} \\ \hline
\texttt{prop.owner != seller}: trade fails & \texttt{test\_trade\_fails\_when\_seller\_does\_not\_own\_property} in tests/test\_trade\_and\_rent.py \\ \hline
\texttt{buyer.balance} $<$ cash\_amount: trade fails & \texttt{test\_trade\_fails\_when\_buyer\_cannot\_afford} in tests/test\_trade\_and\_rent.py \\ \hline
Successful trade: transfer property and adjust balances & \texttt{test\_trade\_succeeds\_and\_transfers\_property\_and\_cash} in tests/test\_trade\_and\_rent.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: auction\_property}} \\ \hline
Bid $\leq 0$: player passes & \texttt{test\_auction\_property\_no\_bids\_and\_with\_winner} (all players bid 0) in tests/test\_game\_ui\_main.py \\ \hline
Bid $<$ highest\_bid + \texttt{AUCTION\_MIN\_INCREMENT}: bid rejected as too low & \texttt{test\_auction\_property\_rejects\_low\_and\_unaffordable\_bids} in tests/test\_game\_ui\_main.py \\ \hline
Bid $>$ \texttt{player.balance}: bid rejected as unaffordable & \texttt{test\_auction\_property\_rejects\_low\_and\_unaffordable\_bids} in tests/test\_game\_ui\_main.py \\ \hline
Valid highest bid exists: winner pays, becomes owner, bank collects & \texttt{test\_auction\_property\_no\_bids\_and\_with\_winner} in tests/test\_game\_ui\_main.py \\ \hline
No valid bids at all: property remains unowned & First part of \texttt{test\_auction\_property\_no\_bids\_and\_with\_winner} in tests/test\_game\_ui\_main.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: \_handle\_jail\_turn}} \\ \hline
Player has jail card and confirms use: card consumed, released, roll and move & \texttt{test\_use\_get\_out\_of\_jail\_free\_card\_with\_confirm\_yes} in tests/test\_jail\_and\_cards.py \\ \hline
Player has no card and declines fine: only jail.turns increments, no movement & \texttt{test\_decline\_all\_options\_increments\_jail\_turn\_counter} in tests/test\_jail\_and\_cards.py \\ \hline
Voluntary fine: player pays fine (up to balance), is released, and moves & \texttt{test\_jail\_turn\_voluntary\_fine\_deducts\_from\_player} in tests/test\_jail\_and\_cards.py \\ \hline
Voluntary fine causes bankruptcy: player eliminated, bank only collects available cash, no move & \texttt{test\_jail\_voluntary\_fine\_can\_bankrupt\_and\_prevent\_movement} in tests/test\_jail\_and\_cards.py \\ \hline
Three skipped turns: mandatory fine, release, move when still solvent & \texttt{test\_jail\_turn\_mandatory\_fine\_after\_three\_turns} in tests/test\_jail\_and\_cards.py \\ \hline
Mandatory fine causes bankruptcy: player eliminated, bank only collects available cash, no move & \texttt{test\_jail\_mandatory\_fine\_bankruptcy\_only\_collects\_available\_cash} in tests/test\_jail\_and\_cards.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.game: \_check\_bankruptcy / check\_bankruptcy and winner/run}} \\ \hline
Player not bankrupt: no elimination & Many tests indirectly (e.g., tax and rent tests where balance stays $\geq 0$), such as \texttt{test\_income\_tax\_reduces\_balance\_but\_not\_eliminate\_when\_affordable} in tests/test\_taxes\_and\_rent.py \\ \hline
Player bankrupt: eliminate, clear properties, remove from players & \texttt{test\_collect\_from\_all\_can\_bankrupt\_and\_eliminate\_other\_players} in tests/test\_bankruptcy\_cards.py, \texttt{test\_pay\_rent\_can\_bankrupt\_tenant} in tests/test\_trade\_and\_rent.py, tax and jail bankruptcy tests in tests/test\_taxes\_and\_rent.py and tests/test\_jail\_and\_cards.py \\ \hline
\texttt{find\_winner} with no players $\rightarrow$ returns \texttt{None} & \texttt{test\_find\_winner\_with\_no\_players\_returns\_none} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
\texttt{find\_winner} chooses player with highest net worth & \texttt{test\_find\_winner\_picks\_highest\_net\_worth} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
\texttt{run} main loop terminates when only one player remains or turn limit reached & \texttt{test\_main\_runs\_game\_entry\_point} and related integration tests in tests/test\_game\_ui\_main.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.board: get\_tile\_type, is\_purchasable, collections}} \\ \hline
\texttt{get\_property\_at} returns \texttt{Property} for known positions, \texttt{None} otherwise & \texttt{test\_get\_property\_and\_tile\_types\_and\_specials} and \texttt{test\_is\_purchasable\_owned\_mortgaged\_and\_collections} in tests/test\_player\_board\_property.py \\ \hline
\texttt{get\_tile\_type}: ``go'', ``property'', ``blank'', special tiles (including ``jail'') & \texttt{test\_get\_property\_and\_tile\_types\_and\_specials} in tests/test\_player\_board\_property.py \\ \hline
\texttt{is\_purchasable}: true for unowned, not-mortgaged property & \texttt{test\_is\_purchasable\_owned\_mortgaged\_and\_collections} in tests/test\_player\_board\_property.py \\ \hline
\texttt{is\_purchasable}: false for mortgaged, owned, or non-property tiles & \texttt{test\_is\_purchasable\_owned\_mortgaged\_and\_collections} in tests/test\_player\_board\_property.py \\ \hline
\texttt{properties\_owned\_by} and \texttt{unowned\_properties} reflect ownership & \texttt{test\_is\_purchasable\_owned\_mortgaged\_and\_collections} in tests/test\_player\_board\_property.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.property: Property, PropertySpec, PropertyGroup}} \\ \hline
\texttt{PropertySpec.as\_tuple} includes name, position, price, rent, group & \texttt{test\_propertyspec\_as\_tuple\_and\_with\_group} and \texttt{test\_propertyspec\_tuple\_and\_with\_group} in tests/test\_player\_board\_property.py \\ \hline
\texttt{with\_group} returns a new spec with updated group & Same tests as above in tests/test\_player\_board\_property.py \\ \hline
\texttt{Property.mortgage}: first call returns mortgage value, second returns 0 & \texttt{test\_property\_mortgage\_unmortgage\_and\_availability} and \texttt{test\_mortgage\_unmortgage\_and\_availability} in tests/test\_player\_board\_property.py \\ \hline
\texttt{Property.unmortgage}: first call returns 110\% value and clears mortgage; second returns 0 & Same as above in tests/test\_player\_board\_property.py \\ \hline
\texttt{Property.is\_available}: true when unowned and not mortgaged; false when mortgaged or owned & \texttt{test\_property\_mortgage\_unmortgage\_and\_availability} and \texttt{test\_mortgage\_unmortgage\_and\_availability} in tests/test\_player\_board\_property.py \\ \hline
\texttt{Property.get\_rent}: base rent vs doubled for full group ownership & \texttt{test\_group\_ownership\_rent\_and\_counts} and \texttt{test\_get\_rent\_full\_group\_and\_mortgage} in tests/test\_player\_board\_property.py \\ \hline
\texttt{Property.get\_rent}: 0 when mortgaged & \texttt{test\_group\_ownership\_rent\_and\_counts} and \texttt{test\_get\_rent\_full\_group\_and\_mortgage} in tests/test\_player\_board\_property.py \\ \hline
\texttt{PropertyGroup.all\_owned\_by}: false for partial, true for full ownership & \texttt{test\_group\_ownership\_rent\_and\_counts} and \texttt{test\_group\_ownership\_and\_counts} in tests/test\_player\_board\_property.py \\ \hline
\texttt{PropertyGroup.get\_owner\_counts} and size & Same group ownership tests in tests/test\_player\_board\_property.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.player: Player helpers and move}} \\ \hline
\texttt{add\_money} / \texttt{deduct\_money} raise \texttt{ValueError} on negative amounts & \texttt{test\_add\_and\_deduct\_negative\_amount\_raises} and \texttt{test\_negative\_add\_and\_deduct\_raise} in tests/test\_player\_board\_property.py \\ \hline
\texttt{go\_to\_jail} sets position and jail status & \texttt{test\_go\_to\_jail\_sets\_position\_and\_status} and \texttt{test\_go\_to\_jail\_and\_status\_line} in tests/test\_player\_board\_property.py \\ \hline
\texttt{status\_line} includes jailed tag when in jail & Same tests as above in tests/test\_player\_board\_property.py \\ \hline
\texttt{add\_property} / \texttt{remove\_property} update \texttt{count\_properties} & \texttt{test\_properties\_helpers\_and\_repr\_and\_status\_line} and \texttt{test\_properties\_and\_count} in tests/test\_player\_board\_property.py \\ \hline
\texttt{\_\_repr\_\_} includes player name & \texttt{test\_properties\_helpers\_and\_repr\_and\_status\_line} in tests/test\_player\_board\_property.py \\ \hline
Move wraps past end of board and awards Go salary once & \texttt{test\_move\_past\_go\_awards\_salary} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline
Move lands exactly on Go (position 0) and awards Go salary once & \texttt{test\_move\_lands\_exactly\_on\_go\_awards\_salary} in tests/test\_winner\_and\_movement\_and\_purchase.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.dice: Dice}} \\ \hline
\texttt{reset} sets \texttt{die1}, \texttt{die2}, and \texttt{doubles\_streak} to 0 & \texttt{test\_reset\_clears\_values\_and\_streak} in tests/test\_dice\_and\_cards.py \\ \hline
\texttt{roll} updates \texttt{doubles\_streak} for doubles and non-doubles & \texttt{test\_roll\_updates\_doubles\_streak\_and\_describe} in tests/test\_dice\_and\_cards.py \\ \hline
\texttt{describe} output includes ``(DOUBLES)'' when appropriate & \texttt{test\_roll\_updates\_doubles\_streak\_and\_describe} in tests/test\_dice\_and\_cards.py \\ \hline
\texttt{\_\_repr\_\_} returns a string containing ``Dice('' & \texttt{test\_roll\_updates\_doubles\_streak\_and\_describe} in tests/test\_dice\_and\_cards.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.cards: CardDeck}} \\ \hline
Drawing from an empty deck returns \texttt{None} and \texttt{cards\_remaining} is 0 & \texttt{test\_empty\_deck\_draw\_and\_peek} in tests/test\_dice\_and\_cards.py \\ \hline
Drawing cycles through cards and updates \texttt{cards\_remaining} correctly & \texttt{test\_draw\_cycles\_through\_cards\_and\_cards\_remaining} in tests/test\_dice\_and\_cards.py \\ \hline
Automatic reshuffle when deck exhausted and index reset & \texttt{test\_auto\_reshuffle\_when\_deck\_exhausted} and \texttt{test\_reshuffle\_resets\_index} in tests/test\_dice\_and\_cards.py \\ \hline
\texttt{peek} does not advance index & \texttt{test\_draw\_cycles\_through\_cards\_and\_cards\_remaining} in tests/test\_dice\_and\_cards.py \\ \hline
\texttt{\_\_len\_\_} and \texttt{\_\_repr\_\_} behave without error & \texttt{test\_empty\_deck\_draw\_and\_peek} and \texttt{test\_len\_and\_repr\_do\_not\_crash} in tests/test\_dice\_and\_cards.py \\ \hline

\multicolumn{2}{l}{\textbf{moneypoly.ui and main}} \\ \hline
UI print helpers and \texttt{format\_currency} & \texttt{test\_print\_helpers\_and\_format\_currency} in tests/test\_game\_ui\_main.py \\ \hline
\texttt{get\_player\_names} / main entrypoint wiring & \texttt{test\_main\_runs\_game\_entry\_point} and related tests in tests/test\_game\_ui\_main.py \\ \hline
\end{longtable}

Taken together, these tables show that the white-box tests are directly derived from the program's control flow and explicitly target all important branches and edge cases across the core MoneyPoly modules.


\subsection*{Detailed Test Explanations and Errors Found}
To ensure the game reliably handles every possible player action and edge case, each test case targets a specific logical pathway. Below is an explanation in simple words of why key tests are needed and the issues they uncovered:

\begin{itemize}
    \item \textbf{Bankruptcy \& Cards Tests (\texttt{test\_cards\_bankruptcy.py}):} Needed to ensure that when a player draws cards like "Birthday" or "Collect From All", the game correctly handles players with zero or negative balances. \textit{Errors Found}: (Error 1 \& 2) The game previously failed to eliminate insolvent players during card events, allowing them to continue playing with negative money.
    
    \item \textbf{Taxes \& Jail Tests (\texttt{test\_taxes.py}, \texttt{test\_jail.py}):} Needed to test edge cases where a player must pay a mandatory fine (like Income Tax or Jail Fine) but doesn't have enough cash. \textit{Errors Found}: (Errors 5, 11, 12, 13) The game used to deduct the full amount leaving the player in negative balance and magically giving the Bank money that didn't exist. Now it only takes what the player has and bankrupts them cleanly.
    
    \item \textbf{Property \& Rent Tests (\texttt{test\_trade.py}):} Needed to verify that rent is properly transferred and that full property groups charge double. \textit{Errors Found}: (Error 7 \& 10) Full-set logic was broken, and rent wasn't being correctly routed from the tenant to the owner, sometimes just disappearing. 
    
    \item \textbf{Movement \& Winner Tests (\texttt{test\_movement.py}):} Needed to ensure passing Go correctly awards exactly $\$200$ and that the winner is chosen by total net worth. \textit{Errors Found}: (Error 3) Go salary was occasionally paid incorrectly on exact landings, and winner selection failed to account for property values.
    
    \item \textbf{Bank \& Auction Tests (\texttt{test\_bank.py}, \texttt{test\_game.py}):} Needed to prevent the bank from accepting invalid inputs (like negative loans) and to make sure auctions reject bids players can't afford. \textit{Errors Found}: (Error 4 \& 8) The bank previously accepted negative amounts which acted as accidental refunds, and allowed unmortgaging properties for free if the player had no money.
    
    \item \textbf{Dice \& Deck Tests (\texttt{test\_dice.py}):} Needed to make sure that the deck reshuffles correctly when empty, rather than crashing the game. \textit{Errors Found}: (Error 6 \& 9) Drawing from an empty deck previously crashed or returned \texttt{None} indefinitely instead of reshuffling the discard pile automatically.

    \item \textbf{Invalid Input Handling Tests (\texttt{test\_movement.py}):} Needed to ensure that users cannot accidentally skip their turn by fat-fingering a key when asked to buy/auction/skip properties. \textit{Errors Found}: (Error 14) The game previously accepted any random symbol and defaulted to skipping. The while loop fix guarantees they provide valid intent.

\end{itemize}

By covering all these edge cases (zero values, large inputs, unexpected negative amounts), the test suite guarantees that every \texttt{if/else} branch behaves correctly under stress, identifying and resolving the 14 critical logical errors listed above. No additional errors were found beyond the 14 documented, as these tests now achieve 100\% branch coverage.
\end{document}
