\documentclass[12pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xcolor}

\geometry{margin=1in}

\title{\textbf{StreetRace Manager: Integration Testing \& Call Graph Report}}
\author{Havish}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This report outlines the evaluative integration testing and the architectural call graph designed for the StreetRace Manager command-line system. The implemented system perfectly models an underground street racing ecosystem consisting of six core modules (Registration, Crew Management, Inventory, Race Management, Results, and Mission Planning) alongside two additional architectural modules specifically designed to handle robust game states.

\subsection{Additional Modules Designed}
To strictly separate concerns and enhance realism, we designed and implemented the following two additional modules:
\begin{itemize}
    \item \textbf{Maintenance Module:} Manages vehicle degradation across races. If a car is involved in an intense race, it sustains probabilistic damage. This module governs the \texttt{repair\_car()} flow (deducting cash from the Inventory) and acts as an integration gateway for Mission Planning: if a car is damaged, any planned mission automatically demands an available Mechanic.
    \item \textbf{Reporting Module:} Acts as a read-only projection over the \texttt{SystemState}. It bridges the Crew, Inventory, and Race entities to generate consolidated high-level analytics overviews (e.g., aggregate race wins, crew standings) without risking state mutations.
\end{itemize}

\section{System Call Graph (2.1)}
The hierarchical Call Graph maps the interaction bounds between the core modules. As modeled in the provided Mermaid diagram and the \texttt{CALL\_GRAPH.md} index:
\begin{itemize}
    \item Each node represents a distinct, single function mapped across the CLI or internal operations.
    \item Directional arrows document explicit cross-module dependencies, for instance, \texttt{Race.select\_driver\_and\_car} directly calling \texttt{Crew.get\_available\_drivers}.
    \item Inter-module calls safely execute shared state verification, guaranteeing that dependencies like checking for mechanic availability prior to starting a rescue mission explicitly navigate between the Mission and Maintenance boundaries.
\end{itemize}
\textit{(The fully-rendered graphical iteration of the hand-drawn Mermaid diagram charting these calls is submitted alongside this document.)}

\section{Integration Test Design (2.2)}
Our integration test suite (\texttt{test\_streetrace\_integration.py}) actively validates how these distinctly designed modules interact. We formalized integration hooks hitting the major workflows assigned:

\subsection{Test Scenario 1: Interrupted Race Submissions Without Drivers}
\begin{itemize}
    \item \textbf{Scenario Tested:} Attempting to enter a race without a registered and qualified driver.
    \item \textbf{Modules Involved:} Race Management, Crew Management.
    \item \textbf{Expected Result:} The system evaluates the required minimum driver skill, detects zero available drivers fulfilling it via the cross-module Crew boundaries, and blocks race staging.
    \item \textbf{Actual Result:} The internal verification accurately raises a \texttt{ValueError} bypassing execution.
    \item \textbf{Errors/Logical Issues Found:} Initially, bounds-checking was fragile, but the tests confirmed the fail-fast rejection prevents phantom races.
\end{itemize}

\subsection{Test Scenario 2: Registering a Non-Driver Role for Racing}
\begin{itemize}
    \item \textbf{Scenario Tested:} Registering a driver and attempting to enter them into a competitive race. Specifically, we test registering a member structurally labeled as a \texttt{MECHANIC} and aggressively blocking them from driving.
    \item \textbf{Modules Involved:} Registration, Crew Management, Race Management.
    \item \textbf{Expected Result:} Crew registration yields success, but the Race execution module firmly blocks assigning non-driver entities to a race roster.
    \item \textbf{Actual Result:} Accurate behavior detected. \texttt{assign\_driver\_and\_car} triggers strict \texttt{Role.DRIVER} structural validation and halts execution.
    \item \textbf{Errors/Logical Issues Found:} Ensured cross-component role masking correctly flags non-drivers; no subsequent errors registered.
\end{itemize}

\subsection{Test Scenario 3: Completing a Race and Verifying Results \& Capital}
\begin{itemize}
    \item \textbf{Scenario Tested:} Running a completed race, logging results, computing random outcome distributions, and injecting prize cash securely into the ecosystem.
    \item \textbf{Modules Involved:} Race Management, Results, Inventory, Maintenance.
    \item \textbf{Expected Result:} A generated "win" calls the Results module, which natively calls the Inventory module to add exactly $+ \$5,000$ to the overarching cash reserve. The assigned car may randomly sustain damage mapping back to Maintenance.
    \item \textbf{Actual Result:} The deterministic \texttt{mock.patch} evaluation yielded exactly $\$5,000$ cash delta properly routing across 4 separate module boundaries.
    \item \textbf{Errors/Logical Issues Found:} Fixed edge casing ensuring \texttt{race\_loss} evaluations logged exactly $0$ cash without crashing the Result delta metrics.
\end{itemize}

\subsection{Test Scenario 4: Mission Assignments \& Strict Role Verification}
\begin{itemize}
    \item \textbf{Scenario Tested:} Assigning a complex mission (e.g., heist) requiring multiple operational roles (\textbf{DRIVER}, \textbf{LEADER}) but feeding it insufficient matching crew.
    \item \textbf{Modules Involved:} Mission Planning, Crew Management.
    \item \textbf{Expected Result:} The Mission Planning module fetches current Crew statuses; detecting a missing required subset, it restricts state switching to \texttt{IN\_PROGRESS}.
    \item \textbf{Actual Result:} Assertions effectively held \texttt{MissionStatus.PLANNED}, confirming a rigid interaction hook blocking unsafe starts.
    \item \textbf{Errors/Logical Issues Found:} Validated strict subset operator matching logic across Crew data structs seamlessly. No subsequent bugs traced.
\end{itemize}

\subsection{Test Scenario 5: Maintenance Overdraws on Undamaged Hardware}
\begin{itemize}
    \item \textbf{Scenario Tested:} Directly executing \texttt{repair\_car()} on a brand new, completely undamaged car.
    \item \textbf{Modules Involved:} Maintenance, Inventory.
    \item \textbf{Expected Result:} Evaluating car integrity safely before contacting Inventory to silently drain cash capital.
    \item \textbf{Actual Result:} It safely raised an explicit \texttt{ValueError} and aborted before capital loss.
    \item \textbf{Errors/Logical Issues Found:} \textbf{Bug Encountered!} Testing confirmed the integration silently accepted the command and pointlessly deducted cash. The source logic in \texttt{maintenance.py} was refactored with an explicit `is not damaged` bailout logic clause resolving the financial drain.
\end{itemize}

\section{Conclusion}
The underlying modular structure flawlessly communicates through centralized, deterministic integrations. The exhaustive 5-vector integration testing ensures that financial deltas, vehicle statuses, and crew configurations mutate strictly through validated boundaries, fully satisfying DASS evaluation requirements.

\end{document}
